---
title: "Regression"
author: "Chinki"
date: "April 23, 2017"
output:
  word_document: default
  pdf_document: default
---
```{r}
# Installing package 
# install.packages("alr4") If required 
# library(alr4)  If reqired 
```
```{r}
#Reading the data from package 
UN11=alr4::UN11
```
Un11 is the data of National health, welfare, and education statistics for 210 places, mostly UN members, but also other areas like Hong Kong that are not independent countries.
```{r}
#Code to get discription of dataset
help("UN11")
```
```{r}
#Scatterplot of fertility and ppgdp
plot(UN11$fertility~UN11$ppgdp,xlab="Per capita gross domestic product in USD",ylab = "Fertility",main="Scatterplot of fertility and ppgdp",col="blue")
```
From the scatterplot, It is easy to conclude that fertility and ppgdp is not linear.
```{r}
# Correlation test 
cor.test(UN11$ppgdp,UN11$fertility)
```
From the boxcox, We can get transformation.
We will use log transformation.
```{r}
#Tranforming log transformation
y=log(UN11$fertility)
x=log(UN11$ppgdp)
```
```{r}
result1=lm(y~x)
summary(result1)
```
y=2.66551+(-0.20715)*x

Next we will look for dignosis of the model.
1).. Normality test
```{r}
r=residuals(result1)
rs=rstandard(result1)
f=fitted.values(result1)
```
```{r}
plot(y~x,xlab="log of ppgdp",ylab="log of fertility",col="red")
```
```{r}
plot(y~x,xlab="log of ppgdp",ylab="log of fertility",col="red")
abline(lm(y~x))
```

```{r}
#plot of residuals and fitted value 
plot(rs~f)
```
```{r}
#Shapiro test for normality 
shapiro.test(rs)
```
As p value is greater than 0.05.So conclude that formality followed by residuals as well as y.

```{r}
#Brown forsytha test for equal variance
result1$group=ifelse(x<8,c("1"),c("2"))
result1$group
```
```{r}
# install.packages("lawstat") if required 
library(lawstat) 
levene.test(r,result1$group)

```
As p value is greter than 0.05. Equal varinace assumption is satisfied.
```{r}
#constant variance test
 # install.packages("lmtest")
library(lmtest)
library(car)
ncvTest(result1)
```
As p value is grester than 0.05. The constant variance assumption is satisfied.

so all the assumptions are good and satisfied. 
This is perfect example for regression.Transformation is working good.

```{r}
library(sqldf)
UN11

un11_Asia=sqldf("select *from UN11 where group='Asia'")

```

