---
title: "Tortoise Dataset_Regression"
author: "Chinki"
date: "May 10, 2017"
output: word_document
---
Ashton et al. (2007) measured the carapace length (in mm) of 18 female gopher
tortoises (Gopherus polyphemus) in Okeeheelee County Park, Florida, and X-rayed
them to count the number of eggs in each.
```{r}
#Reading the data set
Tortoise=read.table("C:/Computational Statistics/3rd Quater/Regression/Lab/tortoise.txt")
colnames(Tortoise)=c("length","eggs")
```
```{r}
#Getting structure of dataset
str(Tortoise)
```
Dataset contains to integer variables.
```{r}
#Getting summary of the dataset
summary(Tortoise)
```
```{r}
plot(Tortoise$length,Tortoise$eggs,ylim = c(0,20),col="red")
abline(lm(Tortoise$eggs~Tortoise$length))
```
```{r}
#Correlation Test
cor.test(Tortoise$eggs,Tortoise$length)
```
Eggs and length is 12% correlated.
```{r}
#Running Simple linera regression
Tortoise_lm=lm(Tortoise$eggs~Tortoise$length)
summary(Tortoise_lm)
```
Model is not significant as given from pvalues.
```{r}
#Running polynomial Regression (Used False for orthogonal polynomial)
Tortoise_lm2=lm(Tortoise$eggs~poly(Tortoise$length,2,raw=FALSE))
summary(Tortoise_lm2)
```
Sencond order of the lenght is significant and model is also significant.

Diagnostics of the model
```{r}
#Getting residuals 
r=residuals(Tortoise_lm2)
plot(Tortoise$length,r)
```
```{r}
length2=Tortoise$length*Tortoise$length
plot(length2,r)
```
```{r}
#Getting fitted value
f=fitted.values(Tortoise_lm2)
plot(f,r)
```
There is not clear representation of any scatterplot ,but seems to symetric.
```{r}
#Boxplot of residuals
boxplot(r)
```
```{r}
#QQ plots 
qqnorm(Tortoise_lm2$residuals)
qqline(Tortoise_lm2$residuals)
```
```{r}
hist(Tortoise_lm2$residuals,col="red")
```
```{r}
shapiro.test(Tortoise_lm2$residuals)
```
Normality condition is satisfied.
Symmetric boxplot with no outliers.
Lack of fitness test
```{r}
#Model with lenght & Length2
R1=lm(Tortoise$eggs~poly(Tortoise$length,2,raw=FALSE))
length1=Tortoise$length
Length2=Tortoise$length^2
F=lm(Tortoise$eggs~factor(length1)+factor(length2))
anova(R1,F)
```
We fail to reject null H0: Y= ??0 +??1X1+??2X1*X1  at 95% level of significant. It apperas that the variable length & length^2 do not contribute significant information to the number of eggs. 

Coefficicent of determination of the model is 35%, which means 35% eggs are explained by the length*length.

As pvalue of length is 0.5408 & Pvalue of lenght*lenght is 0.004, length*lenght is dominating lenght.
```{r}
#Test to drop length
R1=lm(Tortoise$eggs~poly(Tortoise$length,2,raw=FALSE))
F1=lm(Tortoise$eggs~length1+length2)
anova(R1,F1)
```
We fail to reject reject null hypothesis, H0: ??1=0 at the 5% level of significance. It appears that the variables lenght do not contribute significant information to the the number of eggs. 

```{r}
library(ggplot2)
prd=data.frame(length=seq(from=range(Tortoise$length)[1], to=range(Tortoise$length)[2],length.out = 18))
err=predict(Tortoise_lm2,newdata=prd,se.fit=TRUE)
prd$Ici=err$fit-1.96*err$se.fit
prd$fit=err$fit
prd$uci=err$fit+1.96*err$se.fit
ggplot(prd,aes(x=Tortoise$length,y=fit))+geom_smooth(aes(ymin=Ici,ymax=uci),stat="identity")+geom_point(data=Tortoise,aes(x=Tortoise$length,y=eggs))
```


