---
title: "UN11_interactioneffect_Regression model"
author: "Chinki"
date: "May 10, 2017"
output: word_document
---
Un11 is the data of National health, welfare, and education statistics for 210 places, mostly UN members, but also other areas like Hong Kong that are not independent countries.
```{r}
#Reading the data set from R studio
library(alr4)
Un11=alr4::UN11
```

```{r}
#Boxplot of Life Expectancy for each group
boxplot(Un11$lifeExpF~Un11$group,main="Boxplot of life Expectancy for each group",ylab="Life Expectancy",xlab="Group",col="blue")
```
```{r}
#Running a regression model with interaction
un11_lm=lm(lifeExpF~log(ppgdp)+factor(group)+log(ppgdp)*factor(group), data=Un11)
summary(un11_lm)
```
```{r}
#Running a regression model without interaction
un11_lm2=lm(lifeExpF~log(ppgdp)+factor(group), data=Un11)
summary(un11_lm2)
```
Model is significant in both cases.

Test that interaction is required on we can drop.
```{r}
#Anova model
anova(un11_lm,un11_lm2)
```
H0: Beta4=beta5=0
Ha: not all ??s in H0 equal zero
Fail to reject h0 & conclude that interaction effect is not significant in the model so we will drop interaction effect.
```{r}
#Residuals plots
r=residuals(un11_lm2)
f=fitted.values(un11_lm2)
plot(r~f,col="red")
abline(lm(r~f))
```
```{r}
#QQplot of residuals 
rs=rstandard(un11_lm2)
qqnorm(rs)
qqline(rs,col="red")
```
```{r}
#Fitted & rstandazied residual plot
plot(f,rs)
```
```{r}
#Residuals plot together
par(mfrow=c(2,2))
plot(un11_lm2,which=1:4)
```
```{r}
#Regression band 
library(ggplot2)
ggplot(data=UN11,aes(x=log(ppgdp),y=lifeExpF,colours=factor(group)))+stat_smooth(method = lm,fullrange = FALSE)+geom_point()
```


